A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-02-15 submitted_version_(v3.05)_16-02-15/Trick_J1331_modelling.tex
Paper is submitted.

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in the F450W filter.}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in the F814W filter.}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{Lensing images around the galaxy center.}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar kinematics by \citet{SWELLSV}.}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space Telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The black solid line in panel (b) shows the orientation of the major axis. Its length is $10''$ and it marks approximately the region within which we carry out the dynamical modelling. \emph{Panel (c):} Lensing images in the central region of J1331.  An IRAF \emph{ellipse} model was fitted to and then subtracted from the galaxy's F450W surface brightness in panel (a). The (smoothed) residuals within the white square in panel (a) are shown in panel (c). The four bright blobs (A, B, C and D), which are visible in the residuals, are arranged in a typical strong lensing configuration around the center of the galaxy (G). (The configuration of the two additional blobs which lie approximately on a line with A, B and G does not suggest that these blobs are a lensing doublet. They might rather be star-forming regions of a background galaxy.) \emph{Panel (d):} Stellar kinematics along the galaxy's major axis as measured by \citet{SWELLSV}. Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the root mean-square (rms) velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom). The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' \hat{=} 5.2~\text{kpc}$. The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
\label{fig:specialJ1331}
\end{figure*}
%============================================

@@

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
  \caption{MGE and IRAF \emph{ellipse} model for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines). The black line has a length of $10''$ and its orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed circle. \emph{Panel (a):} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b):} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE. This MGE is not used for dynamical modelling because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
\end{figure*}
%============================================

@@

%============================================
\begin{figure}
\centering
  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF. The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots. For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane. We also show the caustic (green solid line) corresponding to the critical curve and the best fit source position (green dot), which are located in the source plane. For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model. The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
\label{fig:bestfitlensmodel}
\end{figure}
%============================================

@@

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
  \caption{Observed light distribution.}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
  \caption{Lens model mass distribution.}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
  \caption{Comparison of mass and light.}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{Comparison of the observed F814W/I-band surface brightness distribution (panel (a) and orange contours) and derived mass distribution from lensing constraints (panel (b) and pink contours). To allow for a qualitative comparison of the contours in panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius, $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$. The Einstein radius is overplotted as red dotted circle. The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours. The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}. We find, that the lens mass model is more roundish than the light distribution. The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
\label{fig:lenslightcompareALL}
\end{figure*}
%============================================

@@

%============================================
\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines). The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively. For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$. The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
  \label{fig:JAM_modelL}
\end{figure}
%============================================

@@

%============================================
\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming ``mass-follows-light'' and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}
%============================================

@@

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
  \label{fig:JAM_modelG}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{Projected local mass-to-light ratio profile and enclosed mass.}
  \label{fig:enclMass_modelG}
\end{subfigure}
\caption{JAM model found by fitting a galaxy model with increasing total mass-to-light ratio profile $\Upsilon_\text{I,tot}(R')$ to the symmetrized $v_\text{rms}$ data (blue dots). The mass distribution is generated by assigning a different mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ to each Gaussian $i$ in the light distribution MGE in Table \ref{tab:MGEF814W}. The $\Upsilon_{\text{I,tot,}i}$ were treated as free fit parameters. \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue dots) and the best fit model (green line). \emph{Panel (b):} Projected total mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model. The best fit mass-to-light ratios $\Upsilon_{\text{I,tot,}i}$ are plotted against $\sigma_i$ for each MGE Gaussian ($i<5$, yellow stars). (The Gaussians $i=4$ and $i=5$ have the same $\Upsilon_{\text{I,tot,}i}$.) Shown is also the enclosed mass inside the projected radius $R'$ on the sky, $M(<R')$ (green line, right axis). The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line); the agreement is very good.}
\label{fig:modelG}
\end{figure*}
%============================================

@@

%============================================
\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution (pdf) sampled with a Monte Carlo Markov Chain (MCMC) (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue, see Equation \eqref{eq:prior_c200}). We find slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.\\The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance matrix of the MCMC samples and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse) confidence. The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
\label{fig:modelB4_triangle}
\end{figure*}
%============================================

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profiles for the best fit models.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{JAM model including a NFW halo and constant velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot). The 12 lines shown correspond to 12 models randomly drawn from the pdf (marked as grey diamonds in Figure \ref{fig:modelB4_triangle}) and their range demonstrates how tight the modelling constraints are. The mean and standard deviation of the pdf, i.e., the "best fit" parameters, are given in Table \ref{tab:modelB4_bestfit}. \emph{Panel (a):} At $R'\lesssim 3.5''$ the symmetrized $v_\text{rms}$ data used in the fit (solid blue points) is shown together with the best fit $v_\text{rms}$ models (red solid lines). At larger radii the non-symmetrized data (open blue dots) is compared to an extrapolation of the best fit models using the surface brightness MGE for the outer regions from Figure \ref{fig:MGEouterRegions} (red dashed lines). \emph{Panel (b):} Shown is the projected enclosed mass profile of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey). At the Einstein radius $R_\text{ein}$ (red dotted line) the Einstein mass $M_\text{ein}$ is overplotted with a 10\% error, which was also included in the fit as additional constraint. Overplotted is also the effective half-light radius (black dotted line) and the blue dashed line marks the radius within which the data and model were fitted.}
\label{fig:modelB4_models}
\end{figure*}
%============================================

@@

%============================================
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve $v_\text{rot}(R')$ (red solid line in middle panel) from the best fit JAM model with NFW halo by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R'\sim3.5''$ (solid blue dots in central panel). The first panel shows the $v_\text{rms}$ data and model analogous to Figure \ref{fig:modelB4_vrms} for the mean parameters in Table \ref{tab:modelB4_bestfit}. The second panel shows the corresponding $v_\text{rot}$ for the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines). The third panel shows simply the velocity dispersion $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and an extrapolation of the JAM model, using the light distribution MGE from Figure \ref{fig:MGEouterRegions} for the outer regions (red dashed lines). The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
\label{fig:modelB4_vrot}
\end{figure}
%============================================

>>>>

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{first_glimpse_450.ps}
  \caption{J1331 in the F450W filter.}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{first_glimpse_814.ps}
  \caption{J1331 in the F814W filter.}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{lens_imgpos.ps}
  \caption{Lensing images around the galaxy center.}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{stellar_kinematics_data.ps}
  \caption{Stellar kinematics by \citet{SWELLSV}.}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space Telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The black solid line in panel (b) shows the orientation of the major axis. Its length is $10''$ and it marks approximately the region within which we carry out the dynamical modelling. \emph{Panel (c):} Lensing images in the central region of J1331.  An IRAF \emph{ellipse} model was fitted to and then subtracted from the galaxy's F450W surface brightness in panel (a). The (smoothed) residuals within the white square in panel (a) are shown in panel (c). The four bright blobs (A, B, C and D), which are visible in the residuals, are arranged in a typical strong lensing configuration around the center of the galaxy (G). (The configuration of the two additional blobs which lie approximately on a line with A, B and G does not suggest that these blobs are a lensing doublet. They might rather be star-forming regions of a background galaxy.) \emph{Panel (d):} Stellar kinematics along the galaxy's major axis as measured by \citet{SWELLSV}. Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the root mean-square (rms) velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom). The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' \hat{=} 5.2~\text{kpc}$. The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
\label{fig:specialJ1331}
\end{figure*}
%============================================

@@

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{1331F814W_MGE_disk_L.ps}
  \caption{MGE and IRAF \emph{ellipse} model for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines). The black line has a length of $10''$ and its orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed circle. \emph{Panel (a):} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b):} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE. This MGE is not used for dynamical modelling because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
\end{figure*}
%============================================

@@

%============================================
\begin{figure}
\centering
  \includegraphics[width=\linewidth]{lens_all_in_one.ps}
\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF. The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots. For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane. We also show the caustic (green solid line) corresponding to the critical curve and the best fit source position (green dot), which are located in the source plane. For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model. The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
\label{fig:bestfitlensmodel}
\end{figure}
%============================================

@@

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{lens_surface_brightness.ps}
  \caption{Observed light distribution.}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{lens_surface_density.ps}
  \caption{Lens model mass distribution.}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{paper_lensmass_brightness_compare.ps}
  \caption{Comparison of mass and light.}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{Comparison of the observed F814W/I-band surface brightness distribution (panel (a) and orange contours) and derived mass distribution from lensing constraints (panel (b) and pink contours). To allow for a qualitative comparison of the contours in panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius, $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$. The Einstein radius is overplotted as red dotted circle. The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours. The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}. We find, that the lens mass model is more roundish than the light distribution. The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
\label{fig:lenslightcompareALL}
\end{figure*}
%============================================

@@

%============================================
\begin{figure}
  \centering
  \includegraphics[height=6cm]{lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines). The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively. For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$. The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
  \label{fig:JAM_modelL}
\end{figure}
%============================================

@@

%============================================
\begin{figure}
  \centering
  \includegraphics[height=6cm]{jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming ``mass-follows-light'' and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}
%============================================

@@

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{jam_G_vrms.ps}
  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
  \label{fig:JAM_modelG}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{jam_G_enclMass.ps}
  \caption{Projected local mass-to-light ratio profile and enclosed mass.}
  \label{fig:enclMass_modelG}
\end{subfigure}
\caption{JAM model found by fitting a galaxy model with increasing total mass-to-light ratio profile $\Upsilon_\text{I,tot}(R')$ to the symmetrized $v_\text{rms}$ data (blue dots). The mass distribution is generated by assigning a different mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ to each Gaussian $i$ in the light distribution MGE in Table \ref{tab:MGEF814W}. The $\Upsilon_{\text{I,tot,}i}$ were treated as free fit parameters. \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue dots) and the best fit model (green line). \emph{Panel (b):} Projected total mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model. The best fit mass-to-light ratios $\Upsilon_{\text{I,tot,}i}$ are plotted against $\sigma_i$ for each MGE Gaussian ($i<5$, yellow stars). (The Gaussians $i=4$ and $i=5$ have the same $\Upsilon_{\text{I,tot,}i}$.) Shown is also the enclosed mass inside the projected radius $R'$ on the sky, $M(<R')$ (green line, right axis). The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line); the agreement is very good.}
\label{fig:modelG}
\end{figure*}
%============================================

@@

%============================================
\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{B4_contour_plot_short.ps}
\caption{Posterior probability distribution (pdf) sampled with a Monte Carlo Markov Chain (MCMC) (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue, see Equation \eqref{eq:prior_c200}). We find slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.\\The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance matrix of the MCMC samples and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse) confidence. The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
\label{fig:modelB4_triangle}
\end{figure*}
%============================================

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profiles for the best fit models.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{JAM model including a NFW halo and constant velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot). The 12 lines shown correspond to 12 models randomly drawn from the pdf (marked as grey diamonds in Figure \ref{fig:modelB4_triangle}) and their range demonstrates how tight the modelling constraints are. The mean and standard deviation of the pdf, i.e., the "best fit" parameters, are given in Table \ref{tab:modelB4_bestfit}. \emph{Panel (a):} At $R'\lesssim 3.5''$ the symmetrized $v_\text{rms}$ data used in the fit (solid blue points) is shown together with the best fit $v_\text{rms}$ models (red solid lines). At larger radii the non-symmetrized data (open blue dots) is compared to an extrapolation of the best fit models using the surface brightness MGE for the outer regions from Figure \ref{fig:MGEouterRegions} (red dashed lines). \emph{Panel (b):} Shown is the projected enclosed mass profile of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey). At the Einstein radius $R_\text{ein}$ (red dotted line) the Einstein mass $M_\text{ein}$ is overplotted with a 10\% error, which was also included in the fit as additional constraint. Overplotted is also the effective half-light radius (black dotted line) and the blue dashed line marks the radius within which the data and model were fitted.}
\label{fig:modelB4_models}
\end{figure*}
%============================================

@@

%============================================
\begin{figure}
\centering
\includegraphics[width=\linewidth]{B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve $v_\text{rot}(R')$ (red solid line in middle panel) from the best fit JAM model with NFW halo by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R'\sim3.5''$ (solid blue dots in central panel). The first panel shows the $v_\text{rms}$ data and model analogous to Figure \ref{fig:modelB4_vrms} for the mean parameters in Table \ref{tab:modelB4_bestfit}. The second panel shows the corresponding $v_\text{rot}$ for the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines). The third panel shows simply the velocity dispersion $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and an extrapolation of the JAM model, using the light distribution MGE from Figure \ref{fig:MGEouterRegions} for the outer regions (red dashed lines). The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
\label{fig:modelB4_vrot}
\end{figure}
%============================================
